---
title: "Salvador SARS-CoV-2 Seroprevalence"
author: "Mariam Fofana"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
# knitr::opts_knit$set(root.dir = here::here())
```

```{r format, echo=FALSE, include=FALSE, warnings=FALSE, results='hide'}
# Load packages and source necessary files

library(abind)
library(ggplot2)
library(fmsb)
library(lme4)
library(GGally)
library(forcats)
library(boot)
library(tigerstats)
library(gam)
library(PrevMap)
library(mgcv)
library(sjstats)
library(influence.ME)
library(tidyverse)
library(dplyr)
library(statmod)
library(reshape2)
library(egg)
library(patchwork)
library(ggpubr)
library(rstatix)
library(mice)
library(miceadds)
library(pan)
library(mediation)
library(knitr)
library(parameters)


# I: LOAD & FORMAT DATA--------------------------------------------------------
dat2 <- dat
  # read.csv("DeIDData", header = T, stringsAsFactors = T)

dat2 <- dat2 %>%
	mutate(inchi = as.factor(dpc >= 1.25)) %>%
	mutate(covidser1 = razao_l45 >= 0.8 & !is.na(razao_l45)) %>%
  mutate(covidser2 = as.numeric(covidser1)) %>%
  mutate(covidser3 = as.factor(covidser2))

# Reset reference levels for categorical variables
dat2<- dat2 %>%
  mutate(ragecat = relevel(agecat, ref = "30-44")) %>%
  mutate(rgender = relevel(gender, ref = "Male")) %>%
  mutate(inccat = relevel(inccat, ref = ">=5")) %>%
  mutate(schooling = relevel(schooling, ref = ">9")) %>%
  mutate(employedyn = relevel(employedyn, "Unemployed")) %>%
  mutate(indid = trunc((as.numeric(pid) - trunc(as.numeric(pid))) * 10 )) %>%
  mutate(u18yn = !is.na(u18cat))

dat2$adyn = as.factor(dat2$age >= 18)

# dataset of household variables only (unique entry per household)
tmpvar2 <- c("hhid", "hsize", "u18yn", "dpc")

dat3 <- subset(dat2, !is.na(covidser2)) 

dat4 <- subset(dat3, indid == 1)[, tmpvar2]

# Subset of just adults (>=18yo)
adudat <- subset(dat3, age >=18)

cbbPalette <- c("#440144FF", "#7ad151ff", "#414487FF", "#22A884FF", "#999999", "#a65c85ff")
agenames <- c("<18", "18-29", "30-44", "45-59", ">=60")

```

## Aim
This analysis describes the seroprevalence of SARS-CoV-2 and associated risk factors in a cohort of residents in Pau da Lima, an urban slum of Salvador, Brazil. The provided code replicates the analyses featured in Fofana et al, using a synthetic dataset designed to approximate the study data.


## Sociodemographic characteristics

Number of individuals with values for the following variables:
  
Age: `r sum(!is.na(dat3$age))`
  
Sex: `r sum(!is.na(dat3$gender))`
  
Daily per capita income: `r sum(!is.na(dat3$dpc))`
  
Ethnicity: `r sum(!is.na(dat3$racecat))`
  
Marital status: `r sum(!is.na(dat3$marriedyn))`
  
Employment: `r sum(!is.na(dat3$employment))`

Employment and per capita income: `r sum(!is.na(dat3$dpc))` & `r sum(is.na(dat3$employment))`


The total sample includes `r nrow(dat3)` individuals with serology results, among `r length(unique(dat3$hhid))` households. 

The sample includes `r sum(dat3$age<18)` children and `r sum(dat3$age>=18)` adults.

Median and IQR for household size: `r summary(dat4$hsize)[3]` [`r summary(dat4$hsize)[2]` - `r summary(dat4$hsize)[5]`]

Median and IQR for daily per capita income: `r summary(dat4$dpc)[3]` [`r summary(dat4$dpc)[2]` - `r summary(dat4$dpc)[5]`]


#### Table of demographic characteristics
```{r desc7, echo=FALSE, warnings=FALSE, results='hide'}
tab1 <- tab2 <- data.frame()
varnames <- c("agecat", "gender", "racecat", "inccat", grep("ultm$", colnames(dat3), value=T))

varnames2 <- c("marriedyn",
              "employment", "schooling")

i<-j<-minrow<-1
for(i in 1: length(varnames)){
  
  eval(str2expression(paste0("subdat <- dat3$",varnames[i])))
  varlev <- levels(subdat)
  numlev <- length(varlev)
  
  tab1[minrow, 1] <- varnames[i]
  tab1[minrow, 2] <- sum(!is.na(subdat))
  
  for(j in 1:numlev){
    currow <- minrow + j - 1
    tab1[currow, 3] <- varlev[j]
    meetlev <- as.logical(subdat == varlev[j])
    tab1[currow, 4] <- sum(meetlev, na.rm=T)
    tab1[currow, 5] <- length(which(meetlev == 1 & dat3$covidser2 == 1))
    tab1[currow, 6] <- length(which(meetlev == 1 & dat3$covidser2 == 0))
    tmp <- prop.test(length(which(meetlev == 1 & dat3$covidser2 == 1)),
                     length(which(meetlev == 1)))
    tab1[currow, 7:8] <- tmp$conf.int[1:2]
    }
  minrow <- minrow + numlev
}
i<-j<-minrow<-1

for(i in 1: length(varnames2)){
  
  eval(str2expression(paste0("subdat <- dat3$",varnames2[i])))
  varlev <- levels(subdat)
  numlev <- length(varlev)
  
  tab2[minrow, 1] <- varnames2[i]
  tab2[minrow, 2] <- sum(!is.na(subdat))
  
  for(j in 1:numlev){
    currow <- minrow + j - 1
    tab2[currow, 3] <- varlev[j]
    meetlev <- as.logical(subdat == varlev[j])
    tab2[currow, 4] <- sum(meetlev, na.rm=T)
    tab2[currow, 5] <- length(which(meetlev == 1 & dat3$covidser2 == 1))
    tab2[currow, 6] <- length(which(meetlev == 1 & dat3$covidser2 == 0))
    tmp <- prop.test(length(which(meetlev == 1 & dat3$covidser2 == 1)),
                     length(which(meetlev == 1)))
    tab2[currow, 7:8] <- tmp$conf.int[1:2]
    }
  minrow <- minrow + numlev
}
colnames(tab1) <- c("Var", "bigN", "cat", "smalln", "pos", "neg", "lb", "ub")
colnames(tab2) <- c("Var", "bigN", "cat", "smalln", "pos", "neg", "lb", "ub")

tab1 <- tab1 %>%
  mutate(proppos = pos/smalln, propneg = neg/smalln)

tab2 <- tab2 %>%
  mutate(proppos = pos/smalln, propneg = neg/smalln)

tab1$Var[is.na(tab1$Var)] <- ""
tab1$bigN[is.na(tab1$bigN)] <- ""

tab2$Var[is.na(tab2$Var)] <- ""
tab2$bigN[is.na(tab2$bigN)] <- ""

tab1 <- tab1[, c(1:6, 9, 7, 8)]
tab2 <- tab2[, c(1:6, 9, 7, 8)]

tab1$proppos <- round(tab1$proppos*100,2)
tab1$ub <- round(tab1$ub*100,2)
tab1$lb <- round(tab1$lb*100,2)

tab2$proppos <- round(tab2$proppos*100,2)
tab2$ub <- round(tab2$ub*100,2)
tab2$lb <- round(tab2$lb*100,2)
```
##### All participants
`r kable(tab1, "simple", col.names = c("Variable", "N", "Category", "Total", "IgG+", "IgG-", "% IgG+", "LB", "UB"))`

##### Adults
`r kable(tab2, "simple", col.names = c("Variable", "N", "Category", "Total", "IgG+", "IgG-", "% IgG+", "LB", "UB"))`

#### Raw seroprevalence in adults vs children
```{r desc5, echo=FALSE, warnings=FALSE, results='hide'}
serch <- dat3$covidser2[which(dat3$age <18)]
serch <- prop.test(sum(serch==1), length(serch))
serad <- dat3$covidser2[which(dat3$age >=18)]
serad <- prop.test(sum(serad==1), length(serad))

```
Children: `r round(serch$est * 100, 2)` [`r round(serch$conf.int[1] * 100, 2)` - `r round(serch$conf.int[1] * 100, 2)`]


Adults: `r round(serad$est * 100, 2)` [`r round(serad$conf.int[1] * 100, 2)` - `r round(serad$conf.int[1] * 100, 2)`]


#### Reported symptoms
```{r desc6, echo=FALSE, warnings=FALSE, results='hide'}
tmptab <- as.table(rowPerc(xtabs(~symptoms + covidser2, data = dat3)))[, -3] 

colnames(tmptab) <- c("IgG negative", "IgG positive")
rownames(tmptab) <- c("No symptoms", "Symptoms")

```

`r kable(tmptab, "simple")`


### Figure 2
```{r fig2a, echo=FALSE, warnings=FALSE, results='hide'}
p2a <- ggplot(dat3, aes(x = as.factor(covidser2), y = age, color = as.factor(covidser2))) +
  geom_violin(alpha = .75, size = 1.5, show.legend = F) +
  geom_jitter(alpha = .25, show.legend = F) +
  scale_x_discrete(labels=c("Negative", "Positive")) +
  labs(x = "SARS-CoV-2 IgG", y = "Age") +
  scale_color_manual(values = cbbPalette[5:6]) +
  theme(legend.position = "none") +
  theme_classic()
```

```{r fig2b, echo=FALSE, warnings=FALSE, results='hide'}
# Panel B
ageneg <- dat3[which(dat3$covidser2 == 0), c("age", "covidser2")]
agepos <- dat3[which(dat3$covidser2 == 1), c("age", "covidser2")]
agenegF <- dat3[which(dat3$covidser2 == 0 & dat3$gender == "Female"), c("age", "covidser2")]
agenegM <- dat3[which(dat3$covidser2 == 0 & dat3$gender == "Male"), c("age", "covidser2")]
ageposF <- dat3[which(dat3$covidser2 == 1 & dat3$gender == "Female"), c("age", "covidser2")]
ageposM <- dat3[which(dat3$covidser2 == 1 & dat3$gender == "Male"), c("age", "covidser2")]
tmp3 <- wilcox.test(ageneg$age, agepos$age)
tmp3F <- wilcox.test(agenegF$age, ageposF$age)
tmp3M <- wilcox.test(agenegM$age, ageposM$age)

mdltmp1 <- gam(covidser2 ~ s(age), data = dat3)
mdltmp1F <- gam(covidser2 ~ s(age), data = dat3[which(dat3$gender == "Female"),])
mdltmp1M <- gam(covidser2 ~ s(age), data = dat3[which(dat3$gender == "Male"),])

testdata1 = data.frame(age = seq(5, 75, by=0.2))
fits1 = predict(mdltmp1, newdata=testdata1, type='response', se=T)
predicts1 = data.frame(testdata1, fits1) %>% 
  mutate(lower = fit - 1.96*se.fit,
         upper = fit + 1.96*se.fit) %>%
  mutate(odds = fit / (1 - fit)) %>%
  mutate(oddlo = lower / (1 - lower))  %>%
  mutate(oddhi = upper / (1 - upper))

testdata1F = data.frame(age = seq(5, 75, by=0.2), gender = "Female")
fits1F = predict(mdltmp1F, newdata=testdata1F, type='response', se=T)
predicts1F = data.frame(testdata1F, fits1F) %>% 
  mutate(lower = fit - 1.96*se.fit,
         upper = fit + 1.96*se.fit) %>%
  mutate(odds = fit / (1 - fit)) 

testdata1M = data.frame(age = seq(5, 75, by=0.2), gender = "Male")
fits1M = predict(mdltmp1M, newdata=testdata1M, type='response', se=T)
predicts1M = data.frame(testdata1M, fits1M) %>% 
  mutate(lower = fit - 1.96*se.fit,
         upper = fit + 1.96*se.fit) %>%
  mutate(odds = fit / (1 - fit)) 

predicts1sex <- rbind(predicts1F, predicts1M) %>%
  mutate(minodd = min(odds, na.rm=T)) %>%
  mutate(oddlo = lower / (1 - lower)) %>%
  mutate(oddhi = upper / (1 - upper)) 

p2b <- ggplot(aes(x=age,y=fit, color=gender),  data=predicts1sex) +
  geom_ribbon(aes(ymin = lower, ymax=upper, fill=gender), alpha=0.25) +
  geom_line(aes(color=gender), size=1.5) +
  labs(x = "Age", y = "Seroprevalence", fill="", color="") +
  theme_classic() + 
  # geom_hline(yintercept = 1, linetype = "dashed") +
   scale_x_continuous(breaks = seq(5,75,5)) +
  scale_y_continuous(limits=c(0, 1))+
  theme(legend.position = c(0.8, 0.95)) +
  scale_color_manual(values = cbbPalette[c(3:4)]) +
  scale_fill_manual(values = cbbPalette[c(3:4)]) 

p2a + p2b + plot_layout(widths = unit(c(7, 7), c('cm', 'cm')), heights = unit(5, "cm"))
```

```{r fig2c, echo=FALSE, warnings=FALSE, results='hide'}
# Panel C
stat.test01<-subset(dat3) %>%
  mutate(inter = interaction(covidser3, agecat)) %>%
  group_by(agecat) %>%
  t_test(hsize ~ covidser3) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance("p.adj") %>%
  add_xy_position(x = "agecat")

p2c<-ggplot(data = dat3, aes(x= covidser3, y=hsize, 
                        group = covidser3, color=covidser3)) +
  geom_boxplot(size = 1) +
  geom_jitter(alpha= 0.2, size = 1) +
  facet_grid(. ~ agecat, switch="x") +
  guides(x="none") +
  # ggtitle("All households") +
  xlab("Age group") +
  ylab("Residents in household") +
  scale_color_manual("SARS-CoV-2 IgG", labels = c("Negative", "Positive"), values = cbbPalette[c(5:6)]) +
  scale_y_continuous(breaks=seq(1,12,1), limits = c(0, 16)) +
  # ggtitle("Household size by age") +
  theme_classic() +
  theme(legend.position = c(0.1, 0.9)) 

```

```{r fig2d, echo=FALSE, warnings=FALSE, results='hide'}
# Panel D
# Compute proportion and CI of seroprevalence in the following groups:
# Age breaks 0, 15, 30, 45, 60
# Presence of children in household
proptable <- data.frame(age = rep(levels(dat3$agecat), 2)) %>%
  mutate(children = rep(c(TRUE, FALSE), each = 5)) %>%
  mutate(tot = NA, pos = NA, prop = NA, lower = NA, upper = NA)

for(i in 1:10){
  proptable$tot[i] <- length(dat3$covidser2[which(dat3$agecat == proptable$age[i] & dat3$u18yn == proptable$children[i])]) 
    proptable$pos[i] <- length(dat3$covidser2[which(dat3$agecat == proptable$age[i] & dat3$u18yn == proptable$children[i] & dat3$covidser2 == 1)]) 
    if(proptable$tot[i] > 0) {tmp <- prop.test(proptable[i, 4], proptable[i, 3])
      proptable$prop[i] <- tmp$estimate
      proptable[i, 6:7] <- tmp$conf.int}
    else {proptable[i, 5:7] <- NA}
}

proptable$age <- factor(proptable$age,levels = agenames)

pval <- data.frame(cbind(age=levels(proptable$age), p=NA, ast=NA))
for(i in 2:5){
 tmp<-proptable[proptable$age==pval$age[i],4:3]
 tmp2<-prop.test(x=tmp$pos, n=tmp$tot)
  pval$p[i] <- tmp2$p.value
  pval$ast[i] <- c("", "*")[(tmp2$p.value<0.05)+1]
}

stat.test0<-subset(dat3, agecat != "<18") %>%
  mutate(inter = interaction(u18yn, agecat)) %>%
  group_by(agecat) %>%
  t_test(covidser2 ~ u18yn) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance("p.adj")  %>%
  add_xy_position(x = "agecat")

p2d<-ggplot() +
  geom_pointrange(data=proptable, mapping = aes(ymin = lower,
                                ymax = upper, 
                                y = prop,
                                x = age,
                                color = children),
                  position = position_dodge(width= 0.2), shape = 16) +
  xlab("Age group") +
  ylab("Seroprevalence") +
  scale_y_continuous(limits = c(0, 0.8)) +
  # geom_text(data=pval, aes(x=age, y=max(proptable$upper, na.rm=T) +0.02, label = ast), size = 8)+
  theme_classic()+
  scale_color_manual("Children in household", labels = c("No", "Yes"), values = cbbPalette[c(1:2)]) +
  theme(legend.position = c(0.3, 0.9)) 

```

```{r fig2e, echo=FALSE, warnings=FALSE, results='hide'}

# Panel E
proptable <- data.frame(adult = rep(c(1, 2), each=3)) %>%
  mutate(children = rep(c("1", "2", "3+"), 2)) %>%
  mutate(tot = NA, pos = NA, prop = NA, lower = NA, upper = NA)

for(i in 1:6){
  proptable$tot[i] <- length(dat3$covidser2[which(as.character(dat3$adcat) == as.character(proptable$adult[i]) & as.character(dat3$u18cat) == as.character(proptable$children[i]))]) 
  proptable$pos[i] <- length(dat3$covidser2[which(as.character(dat3$adcat) == as.character(proptable$adult[i]) & as.character(dat3$u18cat) == as.character(proptable$children[i]) & dat3$covidser2 == 1)]) 
  if(proptable$tot[i] > 0) {tmp <- prop.test(proptable[i, 4], proptable[i, 3])
  proptable$prop[i] <- tmp$estimate
  proptable[i, 6:7] <- tmp$conf.int}
  else {proptable[i, 5:7] <- NA}
}

proptable$adult <- factor(proptable$adult)
proptable$children <- factor(proptable$children)

proptable <- proptable %>%
  mutate(odds = prop / (1-prop)) %>%
  mutate(minodd = min(odds, na.rm = T)) %>%
  mutate(or = odds / minodd) %>%
  mutate(oddlo = (lower / (1 - lower)) / minodd) %>%
  mutate(oddhi = (upper / (1 - upper)) /minodd) %>%
  mutate(inter = interaction(adult, children))

tmplabel <- data.frame(cbind(inter = levels(proptable$inter),
                             adult = rep(c("1 adult", "2 adults"), 3),
                             children = rep(c("1 child", "2 children", ">=3 children"), each=2)))


stat.test2<-subset(dat3, !is.na(u18cat) & adcat %in% c("1", "2")) %>%
  mutate(inter = interaction(u18cat, adcat)) %>%
  # group_by(totad) %>%
  t_test(covidser2 ~ u18cat) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance("p.adj") %>%
  add_xy_position(x = "u18cat") %>%
  mutate(y.position = 1 - seq(0.1, 0.2, 0.05))

p2e<-ggplot() +
  geom_pointrange(data=proptable, mapping = aes(ymin = lower,
                                                ymax = upper, 
                                                y = prop,
                                                x = children,
                                                color=adult),
                  position = position_dodge(width= 0.2), shape = 16) +
  xlab("Number of children in household") +
  scale_x_discrete(labels = c("1", "2", ">=3")) +
  ylab("Seroprevalence") +
  #  geom_text(data=pval, aes(x=adult, y=max(proptable$upper, na.rm=T) +0.02, label = ast), size = 8) +
  # geom_text(data=pval, aes(x=adult, y=max(proptable$upper)+0.5, label=ast), size = 8) +
  scale_y_continuous(limits=c(0, 1)) +
  theme(legend.position = c(0.1, 0.7)) +
  coord_cartesian(clip="off") +
  theme_classic() +
  scale_color_manual("", labels=c("1 adult", "2 adults"), values = cbbPalette[c(1:2)]) +
  stat_pvalue_manual(stat.test2, hide.ns=T, label = "p.adj.signif", tip.length = 0.01) +
  theme(legend.position = c(0.8, 0.2))

p2c + p2d + plot_layout(widths = unit(c(7, 7), c('cm', 'cm')), heights = unit(5, "cm"))

p2e + plot_layout(widths = unit(c(7), c('cm')), heights = unit(5, "cm"))

```

#### Figure 3

```{r fig3, echo=FALSE, warnings=FALSE, results='hide'}
# Figure 3
# Panel A

stat.test3<-subset(adudat, !is.na(employedyn) & !is.na(dpc)) %>%
  mutate(inter = interaction(employedyn, gender)) %>%
  group_by(employedyn) %>%
  t_test(dpc ~ gender) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance("p.adj") %>%
  add_xy_position(x = "employedyn") %>%
  mutate(xmin = c(1.4, 1.4), xmax = c(1.6, 1.6))

p3a<-adudat %>%
  subset(!is.na(employedyn) & !is.na(dpc)) %>%
  mutate(dpc = ifelse(dpc==0, dpc+0.5, dpc)) %>%
  ggplot(aes(x = gender, y = dpc, color = gender,
                       group = gender)) +
  geom_boxplot(alpha = .05, size = 1, width = 1.2) +
  geom_jitter(alpha = .25, size = 1) +
  facet_grid(. ~ employedyn, switch="x") +
  guides(x="none") +
  xlab("Employed") +
  ylab("Income per capita (USD/day)") +
  scale_y_continuous(limits = c(0, 34)) +
  # scale_y_continuous(trans="log2", breaks = c(1.25, 2.5, 5, 10, 20, 40), 
  #                    limits = c(0.25, 50), labels = c("1.25", "2.5", "5", "10", "20", "40")) +
  stat_pvalue_manual(stat.test3, label="p.adj.signif",linetype=0,
                     y.position = 25) +
  theme_classic() +
  scale_color_manual("", values = cbbPalette[c(3,4)]) +
  theme(legend.position = c(0.15, 0.95)) 



# Panel B

proptable <- data.frame(emp = rep(rep(levels(dat3$employedyn), each=2),2)) %>%
  mutate(sex = rep(c("Male", "Female"), each = 4)) %>% 
  mutate(inc = rep(levels(dat3$inchi), 4)) %>% 
  mutate(tot = NA, pos = NA, prop = NA, lower = NA, upper = NA) %>%
  mutate(emp = relevel(factor(emp), "Unemployed")) %>%
  mutate(inc = factor(inc))
  
i<-1
for(i in 1:8){
  proptable$tot[i] <- length(dat3$covidser2[which(dat3$employedyn == proptable$emp[i] & dat3$gender == proptable$sex[i] & dat3$inchi == proptable$inc[i] & dat3$age>=18)]) 
  proptable$pos[i] <- length(dat3$covidser2[which(dat3$employedyn == proptable$emp[i] & dat3$gender == proptable$sex[i] &  dat3$inchi == proptable$inc[i] & dat3$age>=18 & dat3$covidser2 == 1)]) 
  if(proptable$tot[i] > 0) {tmp <- prop.test(proptable[i, 5], proptable[i, 4])
  proptable$prop[i] <- tmp$estimate
  proptable[i, 7:8] <- tmp$conf.int} else {proptable[i, 6:8] <- NA}
}

proptable <- proptable %>%
  mutate(odds = prop / (1-prop)) %>%
  mutate(minodd = min(odds, na.rm = T)) %>%
  mutate(or = odds / minodd) %>%
  mutate(oddlo = (lower / (1 - lower)) / minodd) %>%
  mutate(oddhi = (upper / (1 - upper)) / minodd) %>%
  mutate(inter = interaction(emp, inc))

pval <- data.frame(cbind(inter=levels(proptable$inter), p=NA, ast=NA))
for(i in 1:4){
  tmp<-proptable[proptable$inter==pval$inter[i],5:4]
  tmp2<-prop.test(x=tmp$pos, n=tmp$tot)
  pval$p[i] <- tmp2$p.value
  pval$ast[i] <- c("", "*")[(tmp2$p.value<0.05)+1]
}

stat.test4<-subset(adudat, !is.na(inchi) & !is.na(employedyn)) %>%
  mutate(inter = interaction(employedyn, inchi)) %>%
  group_by(inter) %>%
  t_test(covidser2 ~ gender) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance("p.adj") %>%
  add_xy_position(x = "inter")

tmplabel <- data.frame(cbind(inter = levels(proptable$inter),
                             emp = rep(c("Unemployed", "Employed"), 2),
                             inc = rep(c("<1.25 USD/day", ">=1.25 USD/day"), each=2))) 


p3b<-ggplot() +
  geom_pointrange(data=proptable, mapping = aes(ymin = lower,
                                                ymax = upper, 
                                                y = prop,
                                                x = inter,
                                                color = sex),
                  position = position_dodge(width= 0.2), shape = 16) +
  xlab("Employment") +
  ylab("Seroprevalence") +
  scale_x_discrete("", breaks=NULL) +
  # geom_text(data=pval, aes(x=inter, y=max(proptable$upper)+0.5, label=ast), size = 8) +
  scale_y_continuous(limits=c(-0.06, 1)) +
  geom_text(data=tmplabel, aes(x=inter, y = -0.01, label = emp), size=2.5) +
  geom_text(data=tmplabel, aes(x=inter, y = -0.06, label = inc), size=2.5) +
  coord_cartesian(clip="off") +
  stat_pvalue_manual(stat.test4, hide.ns=T, label = "p.adj.signif", y.position = 0.7,
                     linetype=0) +
  theme_classic() +
  theme(legend.position = c(0.8, 0.95)) +
  scale_color_manual("", values = cbbPalette[c(3,4)]) +
  theme(axis.text=element_text(size=8))

p3a + p3b + plot_layout(widths = unit(c(7, 9), c('cm', 'cm')), heights = unit(5, "cm"))
```


Are children more susceptible to SARS-CoV-2 after adjusting for household clustering and household size?


```{r mlm1, echo=FALSE, warnings=FALSE, results='hide'}

mdl1 <- glmer(covidser2 ~ ragecat + dpc +
              rgender +  + hsize +
                 (1 | hhid),
                 data = dat3, family = binomial, control=glmerControl(optimizer="Nelder_Mead"))
tmpse1 <- sqrt(diag(vcov(mdl1)))
tmpres1 <- cbind(OR = exp(fixef(mdl1)), LL = exp(fixef(mdl1) - 1.96 * tmpse1), UL = exp(fixef(mdl1) + 1.96 * tmpse1))
rownames(tmpres1) <-  c("Intercept", levels(dat3$ragecat)[-1], "Income", "Female gender", "Total residents")

```

```{r table1, echo=FALSE, include=TRUE, warnings=FALSE}  
kable(tmpres1)
```

AIC: `r extractAIC(mdl1)[2]`; ICC: `r performance::icc(mdl1)[1]`


Does the size of the household predict seropositivity among adults better than presence of children does?


```{r mlm2, include=FALSE, results='hide', warnings=FALSE}


mdl2 <- glmer(covidser2 ~ ragecat + dpc +
              rgender +  u18yn + 
                 (1 | hhid),
                 data = adudat, family = binomial, control=glmerControl(optimizer="Nelder_Mead"))
tmpse2 <- sqrt(diag(vcov(mdl2)))
tmpres2 <- cbind(OR = exp(fixef(mdl2)), LL = exp(fixef(mdl2) - 1.96 * tmpse2), UL = exp(fixef(mdl2) + 1.96 * tmpse2))
rownames(tmpres2) <-  c("Intercept", levels(adudat$ragecat)[-(1:2)], "Income",
"Female gender", "Children in household")


mdl3 <- glmer(covidser2 ~ ragecat + dpc +
              rgender +  hsize +
                 (1 | hhid),
                 data = dat3, family = binomial, control=glmerControl(optimizer="Nelder_Mead"))
tmpse3 <- sqrt(diag(vcov(mdl3)))
tmpres3 <- cbind(OR = exp(fixef(mdl3)), LL = exp(fixef(mdl3) - 1.96 * tmpse3), UL = exp(fixef(mdl3) + 1.96 * tmpse3))
rownames(tmpres3) <-  c("Intercept", levels(dat3$ragecat)[-(1)], "Income",
"Female gender", "Total residents in household")

```

```{r table2, echo=FALSE, include=TRUE, warnings=FALSE}  
kable(tmpres2, "simple")

kable(tmpres3, "simple")
```


AIC values for these models are `r extractAIC(mdl2)[2]`, `r extractAIC(mdl3)[2]`.
ICC values are `r performance::icc(mdl2)[2]`, `r performance::icc(mdl3)[2]`.   

### Mediation analysis

Is the effect of presence of children mediated by increased household size?

```{r med1, include=FALSE, results='hide', warnings=FALSE}
# # model-based approach
# dathh <- subset(dat3, indid == 1)
# dathh <- dathh[, c("casanova", "hsize", "u18yn")]
# Mediator model 
med.fit <- glmer(hsize ~ u18yn + age + rsexM +
                 (1 | casanova), 
                 data = adudat, family = poisson)   

# Outcome model
out.fit <- glmer(covidser2 ~ u18yn + age + rsexM + hsize + 
                 (1 | casanova), 
                 data = adudat, family = binomial) 

# Mediation analysis
med.out <- mediate(med.fit, out.fit, treat = "u18yn", mediator = "hsize",  sims = 5000, robustSE = T, dropobs = T)

extract_mediation_summary <- function (x) { 
    smat <- c(x$d0, x$d0.ci, x$d0.p)
    smat <- rbind(smat, c(x$d1, x$d1.ci, x$d1.p))
    smat <- rbind(smat, c(x$z0, x$z0.ci, x$z0.p))
    smat <- rbind(smat, c(x$z1, x$z1.ci, x$z1.p))
    smat <- rbind(smat, c(x$tau.coef, x$tau.ci, x$tau.p))
    smat <- rbind(smat, c(x$n0, x$n0.ci, x$n0.p))
    smat <- rbind(smat, c(x$n1, x$n1.ci, x$n1.p))
    smat <- rbind(smat, c(x$d.avg, x$d.avg.ci, x$d.avg.p))
    smat <- rbind(smat, c(x$z.avg, x$z.avg.ci, x$z.avg.p))
    smat <- rbind(smat, c(x$n.avg, x$n.avg.ci, x$n.avg.p))

    rownames(smat) <- c("ACME (control)", "ACME (treated)", 
                        "ADE (control)", "ADE (treated)", "Total Effect", 
                        "Prop. Mediated (control)", "Prop. Mediated (treated)", 
                        "ACME (average)", "ADE (average)", "Prop. Mediated (average)")
    
    return(smat)
}

medsum <- extract_mediation_summary(summary(med.out))


summary(med.out)

```

`r kable(medsum, col.names = c("Estimate", "LB", "UB", "p"))`



### Adjusted seroprevalence estimates

```{r adj1, eval = FALSE, echo=FALSE, warnings=FALSE, results='hide'}

run_analysis_stan_re <- function(model_script,
                                 dat,
                                 analysis,
                                 coef_eqn,
                                 pos_control,
                                 neg_control,
                                 control_tp,
                                 control_fp,
                                 pop_age_cats_s,
                                 pop_age_cats_c,
                                 n_cores = detectCores() - 2,
                                 redo = F,
                                 chains,
                                 iter,
                                 warmup,
                                 control,
                                 ...) {
  ## Prepare data for analysis
  ana_suffix <- case_when(analysis == "lo" ~ "_lo", # 0.8 threshold
                          analysis == "hi" ~ "_hi", # 1.1 threshold
                          T ~ as.character(NA))
  if (is.na(ana_suffix))
    stop("Unknown analysis parameter, must be one of lo, hi")
  
  # Set analysis data
  ana_dat <- as_tibble(dat)
  
  for (var in c("pos", "neg")) {
    ana_dat[[var]] <- as.numeric(dat[[paste0(var, ana_suffix)]])
  }
  
  # Set model matrix
  X <- model.matrix(as.formula(paste("~", coef_eqn)), data = ana_dat,
                    contrasts.arg= list(age_cat = "contr.treatment"))
  
  # name of the stan output file
  if (!dir.exists('results')) {dir.create('results')}
  stan_out_file <- paste0("stan_fit_", analysis,".rds")
  

    re_model <- stan_model(model_script)
    
    # Unique household ids from 1 to N
    u_hh_ids <- unique(ana_dat$household_id)
    ana_dat$u_household_id <- map_dbl(ana_dat$household_id, ~which(u_hh_ids == .))
    
    # Run stan model
    stan_est <- sampling(re_model,
                         data = list(
                           N_survey = nrow(ana_dat),
                           H = length(u_hh_ids),
                           hh = ana_dat$u_household_id,
                           p_vars = ncol(X),
                           X = X,
                           survey_pos = ana_dat$pos,
                           N_pos_control = pos_control,
                           control_tp = control_tp,
                           N_neg_control = neg_control,
                           control_fp = control_fp
                         ),
                         chains = chains,
                         iter = iter,
                         warmup = warmup,
                         control = control)
    
    saveRDS(stan_est, stan_out_file)
 
  
  ## extract log-likelihoods
  stan_ll <- loo::extract_log_lik(stan_est) %>% loo::loo()
  
  ## extract parameters
  beta <- rstan::extract(stan_est, pars = "beta")[[1]]
  sigma <- rstan::extract(stan_est, pars = "sigma_h")[[1]]
  
  pop_cat_mat_s <- pop_age_cats_s %>%
    model.matrix(as.formula(paste("~", coef_eqn)), data = .,
                 contrasts.arg= list(age_cat = "contr.treatment"))
  pop_cat_mat_c <- pop_age_cats_c %>%
    model.matrix(as.formula(paste("~", coef_eqn)), data = .,
                 contrasts.arg= list(age_cat = "contr.treatment"))
  
  ## compute estimates by age category
  cl <- parallel::makeCluster(n_cores)
  doParallel::registerDoParallel(cl)
  
  pop_cat_p_s <- foreach(i = 1:nrow(pop_cat_mat_s),
                       .combine = rbind,
                       .inorder = F,
                       .packages = c("tidyverse", "foreach")) %dopar%
    {
      foreach(j = 1:nrow(beta),
              .combine = rbind,
              .inorder = T) %do%
        {
          
          # Compute probability integrating across in household random effects
          prob <- integrate(function(x) {
            plogis(qnorm(
              x, beta[j, , drop = F] %*% t(pop_cat_mat_s[i, , drop = F]),
              sigma[j]
            ))
          }, 0, 1)[[1]]
          
          tibble(
            age_cat = pop_age_cats_s$age_cat[i],
            sex = pop_age_cats_s$sex[i],
            pop = pop_age_cats_s$pop[i],
            seropos = prob
          ) %>%
            mutate(sim = j)
        }
    }
  pop_cat_p_c <- foreach(i = 1:nrow(pop_cat_mat_c),
                        .combine = rbind,
                        .inorder = F,
                        .packages = c("tidyverse", "foreach")) %dopar%
    {
      foreach(j = 1:nrow(beta),
              .combine = rbind,
              .inorder = T) %do%
        {
          
          # Compute probability integrating across in household random effects
          prob <- integrate(function(x) {
            plogis(qnorm(
              x, beta[j, , drop = F] %*% t(pop_cat_mat_c[i, , drop = F]),
              sigma[j]
            ))
          }, 0, 1)[[1]]
          
          tibble(
            age_cat = pop_age_cats_c$age_cat[i],
            sex = pop_age_cats_c$sex[i],
            pop = pop_age_cats_c$pop[i],
            seropos = prob
          ) %>%
            mutate(sim = j)
        }
    }
  parallel::stopCluster(cl)

  # Results list
  res <- list(
    beta = rstan::extract(stan_est, pars = "beta")[[1]],
    model_mtx = X,
    sigma_h = rstan::extract(stan_est, pars = "sigma_h")[[1]],
    sens = rstan::extract(stan_est, pars = "sens")[[1]],
    spec = rstan::extract(stan_est, pars = "spec")[[1]],
    obs = nrow(ana_dat),
    pos = sum(ana_dat$pos),
    neg = sum(ana_dat$neg),
    stan_ll = stan_ll,
    pop_cat_p_s = pop_cat_p_s,
    pop_cat_p_c = pop_cat_p_c
  )
  
  return(res)
}

#' @title Post-stratification 
#' @description Post-stratify model-derived age- and sex-specific prevalence to 
#'              population age/sex distribution
#' @return a list with parameter posteriors and results
poststrat <- function(pop_cat_p) {
  ## overall estimate
  overall_re <- pop_cat_p %>%
    mutate(
      var = "Overall",
      val = ""
    ) %>%
    group_by(sim, var, val) %>%
    summarize(p = weighted.mean(seropos, pop)) %>%
    ungroup()
  
  ## age-specific probabilities 
  age_re <- pop_cat_p %>%
    mutate(var = "Age") %>%
    rename(val = age_cat) %>%
    group_by(sim, var, val) %>%
    summarize(p = weighted.mean(seropos, pop)) %>%
    ungroup()
  
  # sex-specific probabilities
  sex_re <- pop_cat_p %>%
    mutate(var = "Sex") %>%
    rename(val = sex) %>%
    group_by(sim, var, val) %>%
    summarize(p = weighted.mean(seropos, pop)) %>%
    ungroup()
  
  # Adults
  ad_re <- pop_cat_p %>%
    filter(age_cat != "<18") %>%
    mutate(var = "Adults", val = "") %>%
    group_by(sim, var, val) %>%
    summarize(p = weighted.mean(seropos, pop)) %>%
    ungroup()
  
  # Children 
  ch_re <- pop_cat_p %>%
    filter(age_cat == "<18") %>%
    mutate(var = "Children", val = "") %>%
    group_by(sim, var, val) %>%
    summarize(p = weighted.mean(seropos, pop)) %>%
    ungroup()
  
  # Stratified by both age and sex 
  full_re <- pop_cat_p %>%
    mutate(var = "Full", val = interaction(age_cat, sex)) %>%
    group_by(sim, var, val) %>%
    summarize(p = weighted.mean(seropos, pop)) %>%
    ungroup()
  
  subset_est = bind_rows(
    overall_re,
    sex_re,
    age_re,
    ad_re,
    ch_re,
    full_re
    )
  
  return(subset_est)
}


# Setup
library(tidyverse)
library(rstan)
library(doMC)
library(gridExtra)
library(parallel)
library(doParallel)
library(bayesplot)

## age cuts
age_cuts <- c(0, 18, 30, 45, 60, 200)
## Stan/JAGS settings, don't need to change
options(mc.cores = parallel::detectCores()-2) ## use all cores but two for this
n_chains <- 4
n_iter <- 1500
n_warmup <- 250
p_delta <- 0.99
n_treedepth <- 20
# Output estimate file names
out_est_file_lo <- "re-seropos_lo.rds"

# Validation data

## EuroImmune Manufacturer insert
## number of positive controls from validation data
pos_control <- 56 
## number of negative controls
neg_control <- 97 
## true positive rate for cases
control_tp_lo <- 54
control_tp_hi <- 51 #lab_val_dat %>%
## false positive rate for controls (1-specificity)
control_fp_lo <- 0 
control_fp_hi <- 0 

# Epi data
## read in data
## All individuals in census
datall <- dat2

datall <- datall %>%
  mutate(age_cat = ordered(agecat, levels = c("<18", "18-29", "30-44", "45-59", ">=60"))) %>%
  rename(sex = sexM) 

## Subset with serology results  
sero_dat <- subset(datall, !is.na(razao_l45)) %>%
  rename(household_id = casanova) %>% 
  group_by(household_id) %>%
  mutate(
    hh_obs = n(),
  ) %>%
  ungroup() %>%
  droplevels() %>%
  mutate(pos_lo = razao_l45 >= 0.8, neg_lo = razao_l45 < 0.8) %>%
  mutate(pos_hi = razao_l45 >= 1.1, neg_hi = razao_l45 < 1.1)

## age categories
agevec <- c("<18", "18-29", "30-44", "45-59", ">=60")

## Age distribution among individuals included in census
pdl_ages <- data.frame(age_lower = c(0, 18, 30, 45, 60),
                       age_upper = c(18, 30, 45, 60, 100),
                       age_cat = factor(c("<18", "18-29", "30-44", "45-59", ">=60")),
                       male = NA,
                       female = NA,
                       total = NA)

for(i in 1:5){
  pdl_ages$male[i] <- nrow(subset(datall, age_cat == agevec[i] & sex == "Male"))
  pdl_ages$female[i] <- nrow(subset(datall, age_cat == agevec[i] & sex == "Female"))
  pdl_ages$total[i] <- nrow(subset(datall, age_cat == agevec[i]))
}

# Age distribution for those with serology results
sero_ages <- data.frame(age_lower = c(0, 18, 30, 45, 60),
                       age_upper = c(18, 30, 45, 60, 100),
                       age_cat = c("<18", "18-29", "30-44", "45-59", ">=60"),
                       male = NA,
                       female = NA,
                       total = NA)

for(i in 1:5){
  sero_ages$male[i] <- nrow(subset(sero_dat, age_cat == agevec[i] & sex == "Male"))
  sero_ages$female[i] <- nrow(subset(sero_dat, age_cat == agevec[i] & sex == "Female"))
  sero_ages$total[i] <- nrow(subset(sero_dat, age_cat == agevec[i]))
}

pdl_ages$age_cat <- ordered(pdl_ages$age_cat, levels = agevec)
sero_ages$age_cat <- ordered(sero_ages$age_cat, levels = agevec)

## find population-level proportions of age and sex
# All in census
pdl_age_cats <- pdl_ages %>%
  group_by(age_cat) %>%
  summarize(
    Male = sum(male),
    Female = sum(female)
  ) %>%
  pivot_longer(
    cols = -age_cat,
    names_to = "sex",
    values_to = "pop"
  ) %>%
  mutate(
    pct = pop / sum(pop)
  ) %>%
  full_join(
    expand_grid(
      sex = c("Female", "Male")
    )
  ) 

# Subset with serology results
sero_age_cats <- sero_ages %>%
  group_by(age_cat) %>%
  summarize(
    Male = sum(male),
    Female = sum(female)
  ) %>%
  pivot_longer(
    cols = -age_cat,
    names_to = "sex",
    values_to = "pop"
  ) %>%
  mutate(
    pct = pop / sum(pop)
  ) %>%
  full_join(
    expand_grid(
      sex = c("Female", "Male")
    )
  ) 


  ## model the overall seropositivity with a random effect for household
  ## Seropositivity threshold = 0.8
  re_seropos_lo <- run_analysis_stan_re(
    model_script = "serosurvey-analysis-re.stan",
    dat = sero_dat,
    analysis = "lo",
    coef_eqn = "sex + age_cat",
    pos_control = pos_control,
    neg_control = neg_control,
    control_tp = control_tp_lo,
    control_fp = control_fp_lo,
    pop_age_cats_s = sero_age_cats,
    pop_age_cats_c = pdl_age_cats,
    chains = n_chains,
    iter = n_iter,
    warmup = n_warmup,
    control = list(
      adapt_delta = p_delta,
      max_treedepth = n_treedepth
    ),
    save_warmup = F,
    seed = 1,
    redo = F
  )
  
  saveRDS(re_seropos_lo, out_est_file_lo)

pop_cat_p_lo_s <- re_seropos_lo$pop_cat_p_s
pop_cat_p_lo_c <- re_seropos_lo$pop_cat_p_c

# Extract prevalence estimates
subset_est_lo_c <- poststrat(pop_cat_p_lo_c)
subset_est_lo_s <- poststrat(pop_cat_p_lo_s)

# results
reslo_c <- subset_est_lo_c %>%
  group_by(var, val) %>%
  summarize(
    `Seroprevalence (95% CI)` = paste0(
      mean(100 * p) %>%
        formatC(2, format = "f"), " (",
      quantile(100 * p, probs = .025) %>%
        formatC(2, format = "f"), "-",
      quantile(100 * p, probs = .975) %>%
        formatC(2, format = "f"), ")"
    ))

reslo_s <- subset_est_lo_s %>%
  group_by(var, val) %>%
  summarize(
    `Seroprevalence (95% CI)` = paste0(
      mean(100 * p) %>%
        formatC(2, format = "f"), " (",
      quantile(100 * p, probs = .025) %>%
        formatC(2, format = "f"), "-",
      quantile(100 * p, probs = .975) %>%
        formatC(2, format = "f"), ")"
    ))

```

#### Within sample
```{r table3, eval= FALSE, echo=FALSE, include=TRUE, warnings=FALSE}  
kable(reslo_s)
```


#### Post-stratified estimates for entire population
```{r table4, eval = FALSE, echo=FALSE, include=TRUE, warnings=FALSE}  
kable(reslo_c)
```